Moral Foundations of U.S. Political News Organizations

### 2021-04-14 manuscript/Partisan Media Manuscript.Rmd
kj manuscript suggestions

@@

#setwd('C:/Users/kayla/Documents/GitHub/Will-Pilot/manuscript')
nsim = 10

@@

# Eliminate Missing Data

@@

@@

#subset with Event=='kav'
exp2_kav ... 
```

>>>>

TO-DO LIST:
1. Introduction/Lit Review for new direction using LIWC instead of MFD (KJ)
2. Write Methods by combine data from Will's thesis and bootstrap method from LangofWar (EB)

@@

setwd('C:/Users/kayla/Documents/GitHub/Will-Pilot/manuscript')
nsim = 100

@@

# Eliminate Missing Data
exp2 <- na.omit(exp2)

@@

# Create group labels
exp2_gs$PartisanLean = ifelse(exp2_gs$PartisanLean=='Conservative', 0, 1)

# Loop over the DVs and create values 
# This saves the difference between groups
r = 1
for(DV in DVs){
  for(group in groups){
    data = subset(exp2_gs, PartisanLean==group) #data name
    f = as.formula(paste(DV,'~1', sep=''))
    bs = bootstrap_values(f,data,nsim)
    table2[r, 1] = DV
    if(group==0){
      table2[r, 2] = mean(bs$mean) #table name all the way down 
      table2[r, 3] = mean(bs$sd)
      ncon = length(na.omit(data[[DV]]))
      table2[r, 9] = quantile(bs$mean, 0.025)
      table2[r, 10] = quantile(bs$mean, 0.975)
    }
    if(group==1){
      table2[r, 4] = mean(bs$mean)
      table2[r, 5] = mean(bs$sd)
      nlib = length(na.omit(data[[DV]]))
      table2[r, 11] = quantile(bs$mean, 0.025)
      table2[r, 12] = quantile(bs$mean, 0.975)
    }
  }
  mdiff = d.ind.t(m1 = table2[r,2], m2 = table2[r,4], 
                sd1 = table2[r,3], sd2 = table2[r,5],
                n1 = ncon, 
                n2 = nlib, 
                a = .05)
  table2[r, 6] = mdiff$d
  table2[r, 7] = mdiff$dlow
  table2[r, 8] = mdiff$dhigh
  r = r + 1
}

@@

#subset with Event=='kav'
exp2_kav  <- subset(exp2, Event == "kav")

# Create group labels
exp2_kav$PartisanLean = ifelse(exp2_kav$PartisanLean=='Conservative', 0, 1)

# Loop over the DVs and create values 
# This saves the difference between groups
r = 1
for(DV in DVs){
  for(group in groups){
    data = subset(exp2_kav, PartisanLean==group) #data name
    f = as.formula(paste(DV,'~1', sep=''))
    bs = bootstrap_values(f,data,nsim)
    table3[r, 1] = DV
    if(group==0){
      table3[r, 2] = mean(bs$mean) #table name all the way down 
      table3[r, 3] = mean(bs$sd)
      ncon = length(na.omit(data[[DV]]))
      table3[r, 9] = quantile(bs$mean, 0.025)
      table3[r, 10] = quantile(bs$mean, 0.975)
    }
    if(group==1){
      table3[r, 4] = mean(bs$mean)
      table3[r, 5] = mean(bs$sd)
      nlib = length(na.omit(data[[DV]]))
      table3[r, 11] = quantile(bs$mean, 0.025)
      table3[r, 12] = quantile(bs$mean, 0.975)
    }
  }
  mdiff = d.ind.t(m1 = table3[r,2], m2 = table3[r,4], 
                sd1 = table3[r,3], sd2 = table3[r,5],
                n1 = ncon, 
                n2 = nlib, 
                a = .05)
  table3[r, 6] = mdiff$d
  table3[r, 7] = mdiff$dlow
  table3[r, 8] = mdiff$dhigh
  r = r + 1
}
```
